Next Trippy Structures\thanks{Supported by organization x.}

### 2019-02-26 paper.tex

\begin{figure}[hbt!]
\includegraphics[width=0.5\textwidth]{experiments/board.eps}
\caption{Comparison of \texttt{board\_X$_{LT}$} queries, with all variants}
\end{figure}

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/start.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/end.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{start\_X$_{LT}$} (a) and \texttt{end\_X$_{LT}$} (b) queries, with all variants}
\end{figure}

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy0.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy1.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (a) and starting time (b) restrictions}
\end{figure}

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy2.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy3.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (a) and starting time (b) restrictions with a fixed ending time restriction}
\end{figure}

@@

>>>>

We have implemented the most adequate queries for \ttctr~and \ctr~from those described in Section~\ref{sec:rq}, and measured their average execution time from 100.000 randomly generated queries on [rellenar detalles de Compostela 2]. In this section we will only discuss four of the possible configurations tested for both \ttctr~and \ctr, with t$_{\Psi}$ values of 32 and 512 combining with WM using either uncompressed bitvectors (\texttt{RG32}) or the most compressed (\texttt{RRR128})\footnote{In case of \ctr, this refers to bitvectors from both \texttt{WML} and \texttt{WMJ}}. These four configurations should be adequate enough to illustrate the space-time trade-offs of our approaches, although the execution times for all tested configurations can be found in the Appendix A.

\begin{figure}[hbt!]
\includegraphics[width=0.5\textwidth]{experiments/board.eps}
\caption{Comparison of \texttt{board\_X$_{LT}$} queries, with all variants}
\label{fig:board}
\end{figure}

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/start.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/end.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{start\_X$_{LT}$} (a) and \texttt{end\_X$_{LT}$} (b) queries, with all variants}
\label{fig:start}
\end{figure}

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy0.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy1.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (a) and starting time (b) restrictions}
\label{fig:xy0}
\end{figure}

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy2.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy3.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (a) and starting time (b) restrictions with a fixed ending time restriction}
\label{fig:xy2}
\end{figure}

@@

\input{appendix.tex}
